---
title: "Influence of demographic characteristic on Covid-19 kinetics"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library(plotly)
library(tidyverse)
library(gganimate)
library(gifski)
```

```{r include=FALSE}
covid_aug <- read_tsv(file = "data/03_covid_aug.tsv")
```


```{r include=FALSE}
covid_aug_by_country <- covid_aug %>% 
  group_by(country) %>% 
  slice(which.max(date)) 
```


### Group 2: Mette Christensen, Mette Christoffersen, Signe Modvig and Hans Jakob Hartling

# Introduction
## 1) Hypothesis including bar chart highlighting Denmark
# Methods
## 2) Overview of dataset including flowchart
## 3) Cleaning and augmentation
## 4) Description of final dataset

# Results
### 5.1) Boxplots + gapminder plots (cases) and KM plots (deaths)
#### 5.1.1) Life exp
#### 5.1.2) Health expenditure
#### 5.1.3) Pollution attributable death rate std
#### 5.1.4) Population living in urban areas
#### 5.1.5) Population aged 60 years old percentage
#### 5.1.6) Respiratory diseases

```{r message=FALSE, warning=FALSE}
#plotting depending variable (x-axis) possibly affecting corona outbreak (y-axis)
ggplot(covid_aug_by_country, aes_string(x="population_aged_60_years_old_percentage", y = 'days_from_dec1_to_100_cases')) +
  geom_point(aes(color=log(gdp_per_capita_us_dollars), size=population_in_thousands_total, alpha=0.5)) + 
  scale_size(range = c(0.5, 20), name="Population", labels = NULL) +
  scale_colour_gradientn(colours=topo.colors(5), name = "GDP per capita") +
  ylab("Days from 1st December to 100 cases") +
  xlab("population_aged_60_years_old_percentage") +
  ggtitle("Development of Corona-pandemic by country") +
  guides(alpha="none")
```


### 5.2) Map
### 5.3) Gif
### 5.4) Shiny app
### 5.5) Cluster/PCA
### 5.6) Sex of leader

# Discussion/Conclusion